Wu-Tang Clan

### 2015-03-20 rmtw/a6/latex8.tex
Added more notes to meth a6

\section{Case Company Description}
Mention the country, size and domain. 
Focus mostly on the API since that's what's relevant to our study.

Also try to get some information on the users of the API. (it might be relevant).

The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study. [Ask Richard: Do you think we can claim that our case is typical, critical, revelatory or unique? Or is our current description adequate?]

@@

Explain why we chose case study compared to for example design research.

\subsection{Summary of methodology}

• Research strategy (research methodology) 
AKA EXPLAIN HOW

@@

>>>>

\section{Case Company Description}
Mention the country, size and domain. 
In domain of surveillance cameras and they develop embedded software for the cameras. 
Focus mostly on the API since that's what's relevant to our study. 
Something about market leader in their domain - and that means that changes to their API could have large consequences.

Also try to get some information on the users of the API. (it might be relevant). %%Not sure if we can get htat now, maybe thorugh the interviews or by asking Imed

The case was selected using convenience sampling \cite{flyvbjerg2006five}, and a maximum variation strategy was used \cite{benbasat1987case}. As such, the goal was to include as many companies as possible in this study. [Note to Richard: Do you think we can claim that our case is typical, critical, revelatory or unique? Or is our current description adequate?]

%%Add why we didn't use other sampling methods for the final handin.

@@

Explain why we chose case study compared to for example design research.
%Thius might not have to be in the proposal

@@

It is importnat that we explain exactly why we chose the collection methods we did. It is also important htat we clearly explain which methods relate to which RQs.

Also explain why for example questionnaire wasn't used.
